Reliable feature point matching

### 2013-08-15 text/main/ch5_experiments.tex
Corrections

\section{Experiments}
For our ideal matching algorithm we would like it to return not just 
some correct matches but all possible correct matches when images 
overlap and no matches at all when they don't.  We would like it to work 
flawlessly not just one a few images but on all possible images, and we 
would expect it to run fast even on when faced with tens of thousands of 
feature points.

@@

To convincingly show that the algorithms work for general cases we need 
to demonstrate good results across a wide range of images.  However if 
we are just given to images and a set of matches, there is no
way to tell which matches are correct and which aren't without going 
through the output by hand and for each match verify that it is correct.  
For any but the simplest cases this becomes prohibitively time 
consuming.

@@

A way to circumvent this problem is to restrict the images we test on to 
image pairs that are linked by a homography. Two images linked by a 
homography are are related in a way that means that any point in the 
first image can be translated a point in the second by a linear 
equation. This holds true for two images where the points they have in 
common are situated on a plan, or in the case that the camera only 
rotated in between images. Figure~\ref{fig:homography_example} shows an 
example of an image pair that can be linked with a homography and 
another that cannot. In the second image pair, the change in camera 
position means that pixels can't be linearly translated from one image 
to another. For example would a pixel on the bell be translated to one 
location while an adjacent pixel on the building in the background would
move differently. For this reason we are constrained in which images 
it's possible to test the algorithms on since we cannot evaluate the 
results if the images are not tied by a homography.

Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a 
set of test images to compare the performance of feature detectors. The 
set covers different types of image variations, such as lighting change, 
blur, rotation, and viewpoint change. Inspired by this dataset (in 
particular the `Graf' image set) and motivated by the need for more 
image pairs featuring viewpoint changes, we have compiled a set of 8 
image pairs consisting of subjects taken from two different angles. The 
images are collected from Flickr's database of images published under a 
creative commons licence and feature murals, which makes it possible to 
relate points in the image pairs with a homography since most of the 
points in the images will be lying on a plane.  The images have been 
cropped to show the same motive and resized to $900\times 600$ pixels.  
This dataset will be referred to as the \emph{Murals} dataset.  
Figure~\ref{fig:murals} shows one image from each pair.

@@

To measure the accuracy of an algorithm we are interested in two values:
Precision and Recall. These measures were introduced in \cite{ke2004pca}
and later used in \cite{mikolajczyk2005performance}. Recall corresponds 
to the number of correct matches over the total amount of possible 
correct matches in between the two images:
\begin{equation*}
	recall = \frac{\# ~ Correct ~ Matches}{\# ~ Total ~ Possible ~ 
	Matches}
\end{equation*}
This measure tells us how thorough we are in finding all possible 
matches that could be made between the two images. To decide whether a 
match is correct, we use the following method:
Given a potential match between two pixels $p_1$ and $p_2$, $m = 
\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
two points satisfy the following criteria:
\begin{equation*}
\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
\end{equation*}
That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
less than a certain threshold (we use $d_{\max}=5$ pixels here). To 
count the number of possible matches we go over all possible 
combinations of feature points between the two images, measure their 
distance and count how many lie within the threshold.
Precision on the other hand is measured by the amount of correct matches
over the total amount of matches returned:
\begin{equation*}
	precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
	~ \# ~ False ~ Matches}
\end{equation*}
This measures how accurate the set of returned matches from the 
algorithm is. An algorithm that returns only a few matches out of many, 
but most of them are correct will have a high precision and a low 
recall, where as an algorithm that returns almost all possible matches, 
both true and false will have a low precision but a high recall. The 
ideal matching algorithm will be both precise but also return as many 
correct matches as possible. However for many applications we only need 
enough correct matches to align to the images, in which case we care 
more about precision than recall.

@@

\begin{figure}[t]
	\begin{subfigure}[c]{0.2\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/graf}
	\end{subfigure}%
	~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[c]{0.8\textwidth}
	\centering
	\includegraphics[width=\columnwidth]{images/result_graf}
	%\caption{Performance on Scharf}
	\end{subfigure}%
	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The 
	plot shows the result of 100 patch pairs generated from the source 
	images shown to the left. The x-axis shows the recall based on the 
accumulated amount of potential matches for all 100 patch pairs. }
	\label{fig:result_graf}
\end{figure}

@@

Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
generated from images 1 and 3 of the \emph{Graf} image set 
(cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
\emph{Ratio}, \emph{MM}, \emph{MMC}, \emph{Isomatch} and \emph{Spectral} 
as a function of the number of matches produced (which is achieved by 
varying thresholds over a certain range). The results show that 
\emph{MM} and \emph{MMC} consistently outperform \emph{Ratio}; 
\emph{MMC} generally lies 2-3 percentage points above \emph{MM} when 
both are performing at optimal accuracy.  The geometric matching methods 
\emph{Isomatch} and \emph{Spectral} outperform \emph{Ratio} but fall 
short of \emph{MM} and \emph{MMC}.

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{images/result_accumulated}
	\caption{Results for 900 patch pairs extracted from the 
	\emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} 
	set.  The x-axis shows the recall based on the accumulated amount of 
potential matches for all patch pairs.}
	\label{fig:result_accumulated}
\end{figure}

\begin{figure}[htb]
	\centering
	\includegraphics[width=1\textwidth]{images/result_viewpoint}
	\caption{Results for viewpoint changes using the \emph{Graf} set 
	from \cite{mikolajczyk2005performance}.  S: img1\&2; M: img1\&3; L: 
	img1\&4; XL: img1\&5.}
	\label{fig:result_viewpoint}
\end{figure}

To further investigate the impact of viewpoint changes, we tested the 
algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
contains 5 images of the same mural taken with gradually increasing 
viewpoint changes.  The first images are almost identical, while the 
last are taken from increasingly different angles. The results from   
\emph{MMC} and \emph{Ratio} as shown in 
Figure~\ref{fig:result_viewpoint}, confirm that \emph{MMC} is generally 
superior to \emph{Ratio} across viewpoint changes. For both methods 
however we see a stark decrease in recall as the viewpoint change 
increases. The performance of \emph{MM} (not shown in the plot) is 
similar to \emph{MMC}.

In order to investigate whether a geometric algorithm can be improved by
pruning the initial matching set, we tested a hybrid algorithm 
\emph{Spectral-MMC} where matches are selected by \emph{MMC} before 
being filtered by \emph{Spectral}. The results are shown in 
Figure~\ref{fig:result_spectral-mmc} and show that \emph{Spectral-MMC} 
not only outperforms \emph{Spectral} but also improves on \emph{MMC} at 
similar recall rates, illustrating how a geometric algorithm can be 
complemented by a reliable non-geometric selection of matches.

\begin{figure}[htb]
	\centering
	\includegraphics[width=1\textwidth]{images/result_spectral-mmc}
	\caption{Results for filtering matches with \emph{MMC} before 
	applying the \emph{Spectral} algorithm. The algorithm is tested on 
900 patch pairs extracted from the \emph{Murals} dataset and the image 
pair 1\&3 from the \emph{Graf} set. The x-axis shows the recall based on 
the accumulated amount of potential matches for all patch pairs.}
	\label{fig:result_spectral-mmc}
\end{figure}

Finally, as an example of a real life use case, 
Figure~\ref{fig:result_pitts} shows the results on 100 patch pairs 
generated from a typical holiday photo shot 
(Figure~\ref{fig:pitts_source}) featuring occlusion and a slight 
viewpoint change from the Gallagher dataset \cite{gallagher2008}.  The 
performance is comparable to the murals, despite the lack of a simple 
homographic mapping between the images.

@@

As for speed, Table~\ref{table:running_times} shows the running time of 
the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
These numbers should be taken with a grain of salt, given that much of 
the code behind \emph{MMC} and \emph{Isomatch} is implemented in Python, 
whereas \emph{MM} and \emph{Ratio} make use of OpenCV to execute 
computationally intensive operations in C++, which makes them much 
faster.

>>>>

\section{Experiments}
For our ideal matching algorithm we would like it to return not just 
some correct matches but all possible correct matches when images 
overlap and no matches at all when they don't.  We would like it to work 
flawlessly not just on a few images but on all possible images, and we 
would expect it to run fast even when faced with tens of thousands of 
feature points.

@@

To convincingly show that the algorithms work for general cases we need 
to demonstrate good results across a wide range of images.  However if 
we are just given two images and a set of matches, there is no
way to tell which matches are correct and which aren't without going 
through the output by hand and for each match verify that it is correct.  
For any but the simplest cases this becomes prohibitively time 
consuming.

@@

A way to circumvent this problem is to restrict the images we test on to 
image pairs that are linked by a homography. Two images linked by a 
homography are related in a way that means that any point in the first 
image can be translated a point in the second by a affine equation. This 
holds true for two images where the points they have in common are 
situated on a plan, or in the case that the camera only rotated in 
between images.  Figure~\ref{fig:homography_example} shows an example of 
an image pair that can be linked with a homography and another that 
cannot. In the second image pair, the change in camera position means 
that pixels can't be linearly translated from one image to another. For 
example a pixel on the bell would be translated to one location while an 
adjacent pixel on the building in the background would
move differently. For this reason we are constrained in which images 
it's possible to test the algorithms on since we cannot evaluate the 
results if the images are not tied by a homography.

Mikolajczyk and Schmid  \cite{mikolajczyk2005performance} introduced a 
set of test images to compare the performance of feature detectors. The 
set covers different types of image variations, such as lighting change, 
blur, rotation, and viewpoint change. Inspired by this dataset (in 
particular the `\emph{Graf}' image set) and motivated by the need for 
more image pairs featuring viewpoint changes, we have compiled a set of 
8 image pairs consisting of subjects taken from two different angles.  
The images are collected from \emph{Flickr's} database of images 
published under a \emph{Creative Commons Licence} and feature murals, 
which makes it possible to relate points in the image pairs with a 
homography since most of the points in the images will be lying on a 
plane.  The images have been cropped to show the same motive and resized 
to $900\times 600$ pixels.  This dataset will be referred to as the 
\emph{Murals} dataset.  Figure~\ref{fig:murals} shows one image from 
each pair.

@@

To measure the accuracy of an algorithm we are interested in two values:
Recall and Precision. These measures were introduced in \cite{ke2004pca}
and later used in \cite{mikolajczyk2005performance}. Recall corresponds 
to the number of correct matches over the total amount of possible 
correct matches in between the two images:
\begin{equation*}
	Recall = \frac{\# ~ Correct ~ Matches}{\# ~ Total ~ Possible ~ 
	Matches}
\end{equation*}
This measure tells us how thorough we are in finding all possible 
matches that could be made between the two images. To decide whether a 
match is correct, we use the following method:
Given a potential match between two pixels $p_1$ and $p_2$, $m = 
\left(p_1, p_2\right)$, and a homography $H$ relating the two images 
$I_1$ and $I_2$, we can calculate if $m$ is an inlier by checking if the 
two points satisfy the following criteria:
\begin{equation*}
\left\vert H p_1 - p_2 \right\vert + \left\vert H^{-1}p_2 - p_1 \right\vert < d_{\max}
\end{equation*}
That is, the distance between $p_1$ translated to $I_2$ and $p_2$ 
\emph{plus} the distance between $p_2$ translated to $I_1$ should be 
less than a certain threshold (we use $d_{\max}=5$ pixels here). To 
count the number of possible matches we go over all possible 
combinations of feature points between the two images, measure their 
distance and count how many lie within the threshold.
Precision on the other hand is measured by the amount of correct matches
over the total amount of matches returned:
\begin{equation*}
	Precision = \frac{\# ~ Correct ~ Matches}{\# ~ Correct ~ Matches ~ + 
	~ \# ~ False ~ Matches}
\end{equation*}
This measures how accurate the set of returned matches from the 
algorithm is. An algorithm that returns only a few matches out of many, 
but most of them are correct will have a high Precision and a low 
Recall, where as an algorithm that returns almost all possible matches, 
both true and false will have a low Precision but a high Recall. The 
ideal matching algorithm will be both precise but also return as many 
correct matches as possible. However for many applications we only need 
enough correct matches to align to the images, in which case we care 
more about Precision than Recall.

@@

\begin{figure}[t]
	\begin{subfigure}[c]{0.2\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/graf}
	\end{subfigure}%
	~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[c]{0.8\textwidth}
	\centering
	\includegraphics[width=\columnwidth]{images/result_graf}
	%\caption{Performance on Scharf}
	\end{subfigure}%
	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The 
	plot shows the result of 100 patch pairs generated from the source 
	images shown to the left. The x-axis shows the Recall based on the 
accumulated amount of potential matches for all 100 patch pairs. }
	\label{fig:result_graf}
\end{figure}

@@

Figure~\ref{fig:result_graf} shows the results for 100 patch pairs 
generated from images 1 and 3 of the \emph{Graf} image set 
(cf.~Figure~\ref{fig:Graf}). The plot compares the accuracy of 
\emph{Ratio}, \emph{MM}, \emph{MMC}, \emph{Isomatch} and \emph{Spectral} 
as a function of the number of matches produced (which is achieved by 
varying thresholds over a certain range). The results show that 
\emph{MM} and \emph{MMC} consistently outperform \emph{Ratio}, 
\emph{MMC} generally lies 2-3 percentage points above \emph{MM} when 
both are performing at optimal accuracy.  The geometric matching methods 
\emph{Isomatch} and \emph{Spectral} outperform \emph{Ratio} but fall 
short of \emph{MM} and \emph{MMC}.

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{images/result_accumulated}
	\caption{Results for 900 patch pairs extracted from the 
	\emph{Murals} dataset and the image pair 1\&3 from the \emph{Graf} 
	set.  The x-axis shows the Recall based on the accumulated amount of 
potential matches for all patch pairs.}
	\label{fig:result_accumulated}
\end{figure}

\begin{figure}[htb]
	\centering
	\includegraphics[width=1\textwidth]{images/result_viewpoint}
    \caption{Results for viewpoint changes using the \emph{Graf} set 
    from \cite{mikolajczyk2005performance}.  S: img1 \& 2; M: img1 \& 3; 
    L: img1 \& 4; XL: img1 \& 5.}
	\label{fig:result_viewpoint}
\end{figure}

To further investigate the impact of viewpoint changes, we tested the 
algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
contains 5 images of the same mural taken with gradually increasing 
viewpoint changes.  The first images are almost identical, while the 
last are taken from increasingly different angles. The results from   
\emph{MMC} and \emph{Ratio} as shown in 
Figure~\ref{fig:result_viewpoint}, confirm that \emph{MMC} is generally 
superior to \emph{Ratio} across viewpoint changes. For both methods 
however we see a stark decrease in Recall as the viewpoint change 
increases. The performance of \emph{MM} (not shown in the plot) is 
similar to \emph{MMC}.

In order to investigate whether a geometric algorithm can be improved by
pruning the initial matching set, we tested a hybrid algorithm 
\emph{Spectral-MMC} where matches are selected by \emph{MMC} before 
being filtered by \emph{Spectral}. The results are shown in 
Figure~\ref{fig:result_spectral-mmc} and show that \emph{Spectral-MMC} 
not only outperforms \emph{Spectral} but also improves on \emph{MMC} at 
similar Recall rates, illustrating how a geometric algorithm can be 
complemented by a reliable non-geometric selection of matches.

\begin{figure}[htb]
	\centering
	\includegraphics[width=1\textwidth]{images/result_spectral-mmc}
	\caption{Results for filtering matches with \emph{MMC} before 
	applying the \emph{Spectral} algorithm. The algorithm is tested on 
900 patch pairs extracted from the \emph{Murals} dataset and the image 
pair 1\&3 from the \emph{Graf} set. The x-axis shows the Recall based on 
the accumulated amount of potential matches for all patch pairs.}
	\label{fig:result_spectral-mmc}
\end{figure}

Finally, as an example of a real life use case, 
Figure~\ref{fig:result_pitts} shows the results on 100 patch pairs 
generated from a typical holiday photo shot 
(Figure~\ref{fig:pitts_source}) featuring occlusion and a slight 
viewpoint change from the \emph{Gallagher} dataset \cite{gallagher2008}.  
The performance is comparable to the murals, despite the lack of a 
simple homographic mapping between the images.

@@

As for speed, Table~\ref{table:running_times} shows the running time of 
the four algorithms over 100 image pairs of $250\!\times\!250$ pixels.  
These numbers should be taken with a grain of salt, given that much of 
the code behind \emph{MMC} and \emph{Isomatch} is implemented in 
\emph{Python}, whereas \emph{MM} and \emph{Ratio} make use of 
\emph{OpenCV} to execute computationally intensive operations in 
\emph{C++}, which makes them much faster.

### 2013-08-15 text/main/ch6_applications.tex
Corrections

In many areas of computer vision matching local feature points is a key 
component, and matching algorithms have applications in problems such as
scene matching, object recognition, near duplicate detection and 
panorama recognition. To show the practical applications of the proposed 
matching algorithms, \emph{MM} and \emph{MMC}, we use show how they 
improve existing methods in near duplicate detection and panorama 
recognition. These two problems were chosen because they both involve 
matching images that might or might not overlap. These cases requires 
matching algorithms that limit false positives since the alternative 
would be to select the top $n$ matches which would make it hard to 
distinguish adjacent or duplicate images from non-adjacent or dissimilar
image pairs. Near duplicate detection also constraints normal matching 
algorithms from relying on geometric assumptions, since we have very few
guarantees between two potential near duplicates that they should be 
matched using any particular geometric heuristic. In this section, we 
will first see \emph{MMC} applied to panorama recognition and alignment,
and next \emph{MM} and \emph{MMC} applied to near duplicate detection.

@@

\begin{figure}[h]
	\begin{subfigure}[t]{0.9\textwidth}
		\centering
        \includegraphics[width=\textwidth]{images/pano_wide}
        \label{fig:pano_images}
		\caption{Source images}
    \end{subfigure}%
	\\
	\centering
    \begin{subfigure}[b]{0.4\textwidth}
		\includegraphics[width=\textwidth]{images/panorama-autostitch}
        \label{fig:pano_autostitch}
		\caption{Panorama by Autostitch}
    \end{subfigure}%
	~%add desired spacing between images, e. g. ~, \quad, \qquad
	%(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
		\includegraphics[width=\textwidth]{images/panorama-MMC}
		\caption{Panorama by MMC}
		\label{fig:pano_MMC}
	\end{subfigure}%
    \caption{An example of a difficult case for panorama recognition and 
        alignment.  In a) the source images used to generate the 
        panorama are displayed.\ b) shows the result of the Autostitch 
        program from \cite{brown2007automatic} which fails to combine 
        all images, while c) demonstrates the result of the simple 
        panorama stitcher
	using the proposed MMC algorithm. Here the two left images are 
correctly linked}
    \label{fig:pano_example}
\end{figure}

@@

Figure~\ref{fig:pano_example} shows an example where the added accuracy 
of MMC enables us to correctly recognize and align source images that 
fail to be combined by Autostitch, a program using the algorithm 
proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
case the matching algorithm used in Autostitch fails to find sufficient 
matches between two images pairs to correctly position them and 
consequently doesn't produce a panorama containing all images as a 
result.

@@

\section{Near Duplicate Detection}
If we look at two images, we can often easily tell if one image 
resembles the other enough to be redundant in a photo album. In computer 
vision this task is nontrivial because our idea of a duplicate image 
might only require there being some object or scene in common between 
the image pair. In addition the object or scene might have been taken 
from a different angle and under different camera settings. Facing these 
challenges, work has been done trying to reliably recognize duplicates 
both with regards to corporate intellectual property as well as consumer 
photo albums.  A company might be interested in finding images that are 
derived from their intellectual property, while it allows consumers 
taking vacation photos to automatically grouping duplicate images which 
allows for easier photo organization.

\begin{figure}[h]
	\includegraphics[width=\textwidth]{images/near_duplicate_example}
	\caption{Example of a near duplicate image pair from the 
	California-nd dataset \cite{jinda2012california}}
	\label{fig:near_duplicate}
\end{figure}

@@

The \emph{PhotoCluster} method introduced by Vonikakis et al.  
\cite{vas2013cluster} shows the best clustering performance on the 
California-nd dataset \cite{jinda2012california} which contains a set of
annotated vacation images similar to a typical photo album in a consumer
product. \emph{PhotoCluster} works by grouping images in several steps 
using first image meta data and global features to obtain a set of 
proposed clusters. Then local features are used to find the best 
matching images in these proposed clusters yielding the final groups of 
near duplicate images. To show the viability of \emph{MM} and \emph{MMC} 
in the application of near duplicated detection, we modify the 
PhotoCluster method to use the proposed algorithms for matching images 
instead of \emph{Ratio} which was previously used. The experiments were 
performed as documented in \cite{vas2013cluster}, however due to the 
running time of \emph{MMC} it is intractable to calculate the test 
scores on full scale images. To showcase the performance of \emph{MMC} 
we add a test case using images resizes to 10\% of their original size.

\begin{table}[htb]
\caption{Results from Near Duplicate Detection}
\label{table:ndd}
	\centering
%	\small
\begin{tabular}{r*{3}{r}}
\hline
F1 score & \emph{Ratio} & \emph{MM} & \emph{MMC}   \\
	\noalign{\smallskip}
	%
    10\% Scale: & 0.5013 & 0.5990 & 0.5785 \\
    100\% Scale: & 0.0 & 0.0 & --- \\
	\hline
\end{tabular}
\end{table}

The results of the comparison can be seen in Table~\ref{table:ndd}. It 
shows that \emph{MM} improves performance by 19.49\% over the original 
framework using \emph{Ratio} to match images. For comparison 
\emph{PhotoCluster} improves on the results of Xmatch 
\cite{zhao2009scale}, the second best performing algorithm on the 
California-nd dataset according to \cite{vas2013cluster}, with 2.52\%.

>>>>

In many areas of computer vision matching local feature points is a key 
component, and matching algorithms have applications in problems such as
scene matching, object recognition, near duplicate detection and 
panorama recognition. To show the practical applications of the proposed 
matching algorithms, \emph{MM} and \emph{MMC}, we show how they improve 
existing methods in near duplicate detection and panorama recognition. 
These two problems were chosen because they both involve matching images 
that might or might not overlap. These cases requires matching 
algorithms that limit false positives since the alternative would be to 
select the top $n$ matches which would make it hard to distinguish 
adjacent or duplicate images from non-adjacent or dissimilar
image pairs. Near duplicate detection also constraints normal matching 
algorithms from relying on geometric assumptions, since we have very few
guarantees between two potential near duplicates that they should be 
matched using any particular geometric heuristic. In this section, we 
will first see \emph{MMC} applied to panorama recognition and alignment,
and next \emph{MM} and \emph{MMC} applied to near duplicate detection.

@@

\begin{figure}[h]
	\begin{subfigure}[t]{0.9\textwidth}
		\centering
        \includegraphics[width=\textwidth]{images/pano_wide}
        \label{fig:pano_images}
		\caption{Source images}
    \end{subfigure}%
	\\
	\centering
    \begin{subfigure}[b]{0.4\textwidth}
		\includegraphics[width=\textwidth]{images/panorama-autostitch}
        \label{fig:pano_autostitch}
		\caption{Panorama by \emph{Autostitch}}
    \end{subfigure}%
	~%add desired spacing between images, e. g. ~, \quad, \qquad
	%(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.4\textwidth}
		\includegraphics[width=\textwidth]{images/panorama-MMC}
		\caption{Panorama by MMC}
		\label{fig:pano_MMC}
	\end{subfigure}%
    \caption{An example of a difficult case for panorama recognition and 
        alignment.  In a) the source images used to generate the 
        panorama are displayed.\ b) shows the result of the \emph{Autostitch} 
        program from \cite{brown2007automatic} which fails to combine 
        all images, while c) demonstrates the result of the simple 
        panorama stitcher
	using the proposed MMC algorithm. Here the two left images are 
correctly linked}
    \label{fig:pano_example}
\end{figure}

@@

Figure~\ref{fig:pano_example} shows an example where the added accuracy 
of MMC enables us to correctly recognize and align source images that 
fail to be combined by \emph{Autostitch}, a program using the algorithm 
proposed by Brown and Lowe \cite{brown2007automatic}. In this particular
case the matching algorithm used in \emph{Autostitch} fails to find sufficient 
matches between two images pairs to correctly position them and 
consequently doesn't produce a panorama containing all images as a 
result.

@@

\section{Near Duplicate Detection}
If we look at two images, we can often easily tell if one image 
resembles the other enough to be redundant in a photo album. In computer 
vision this task is nontrivial because our idea of a duplicate image 
might only require that there is some object or scene in common between 
the image pair. In addition the object or scene might have been taken 
from a different angle and under different camera settings. Facing these 
challenges, work has been done trying to reliably recognize duplicates 
both with regards to corporate intellectual property as well as consumer 
photo albums.  A company might be interested in finding images that are 
derived from their intellectual property, while it allows consumers 
taking vacation photos to automatically grouping duplicate images which 
allows for easier photo organization.

\begin{figure}[h]
	\includegraphics[width=\textwidth]{images/near_duplicate_example}
	\caption{Example of a near duplicate image pair from the 
	\emph{California-nd} dataset \cite{jinda2012california}}
	\label{fig:near_duplicate}
\end{figure}

@@

The \emph{PhotoCluster} method introduced by Vonikakis et al.  
\cite{vas2013cluster} shows the best clustering performance on the 
\emph{California-nd} dataset \cite{jinda2012california} which contains a set of
annotated vacation images similar to a typical photo album in a consumer
product. \emph{PhotoCluster} works by grouping images in several steps 
using first image meta data and global features to obtain a set of 
proposed clusters. Then local features are used to find the best 
matching images in these proposed clusters yielding the final groups of 
near duplicate images. To show the viability of \emph{MM} and \emph{MMC} 
in the application of near duplicated detection, we modify the 
PhotoCluster method to use the proposed algorithms for matching images 
instead of \emph{Ratio} which was previously used. The experiments were 
performed as documented in \cite{vas2013cluster}, however due to the 
running time of \emph{MMC} it is intractable to calculate the test 
scores on full scale images.

\begin{table}[htb]
\caption{Results from Near Duplicate Detection}
\label{table:ndd}
	\centering
%	\small
\begin{tabular}{r*{3}{r}}
\hline
Algorithm & \emph{Ratio} & \emph{MM} & \emph{MMC}   \\
	\noalign{\smallskip}
	%
    F1 score: & 0.5013 & 0.5990 & 0.6053 \\
    \hline
\end{tabular}
\end{table}

The results of the comparison can be seen in Table~\ref{table:ndd}. It 
shows that \emph{MM} and \emph{MMC} improves performance by 19.49\% and 
20.75\% respectively over the original framework using \emph{Ratio} to 
match images.

### 2013-08-15 text/main/ch7_summary.tex
Corrections

This thesis has addressed the problem of matching feature points without 
using geometrical constraints, proposing \emph{Mirror Match (MM)} and 
\emph{Mirror Match with Clustering (MMC)}.  The two algorithms share the 
common idea that feature points should have better matches in another 
image than in the image they came from to be considered good matches.  
\emph{MMC} further improves on this idea by using the structure of the 
similarity graph of the feature points.

@@

The practical application of \emph{MM} and \emph{MMC} is demonstrated by 
applying the algorithms to the problems of near duplicate detection and 
for the case of \emph{MMC} to panorama recognition and alignment. For 
the case of near duplicate detection, \emph{MMC} provides an 8.02\% 
improvement over \emph{Ratio} in a near duplicate detection framework 
making use of local features. Similarly for panorama recognition and 
alignment a simple panorama stitching method based on \emph{MMC} 
succeeds in cases where \emph{Autostitch} is unable to recognize and 
align the source images correctly. Both applications illustrate the 
central role that performance of the matching algorithm has on tasks 
that makes use of local features to match image pairs with potential 
overlap.
%

>>>>

This thesis address the problem of matching feature points without using 
geometrical constraints, proposing \emph{Mirror Match (MM)} and 
\emph{Mirror Match with Clustering (MMC)}.  The two algorithms share the 
common idea that feature points should have better matches in another 
image than in the image they came from to be considered good matches.  
\emph{MMC} further improves on this idea by using the structure of the 
similarity graph of the feature points.

@@

The practical application of \emph{MM} and \emph{MMC} is demonstrated by 
applying the algorithms to the problems of near duplicate detection and 
for the case of \emph{MMC} to panorama recognition and alignment. For 
the case of near duplicate detection, \emph{MMC} provides an 20.75\% 
improvement over \emph{Ratio} in a near duplicate detection framework 
making use of local features. Similarly for panorama recognition and 
alignment a simple panorama stitching method based on \emph{MMC} 
succeeds in cases where \emph{Autostitch} is unable to recognize and 
align the source images correctly. Both applications illustrate the 
central role that performance of the matching algorithm has on tasks 
that makes use of local features to match image pairs with potential 
overlap.
%
